Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
finished section of introduction

Digital maps such as Google Maps and OpenStreetMap 
support zooming by displaying maps at different levels. 
This discrete strategy may results in sudden changes, which annoy users.
To provide better zooming experience, 
we try to produce a sequence of maps 
with small incremental changes.
This process is known as \emph{continuous generalization}.

A way to realize continuous generalization is to use morphing.
Often, a start map and a goal map, 
respectively at a larger scale and a smaller scale, 
are used as input, 
and then maps at intermediate scales are produced 
while the start map is morphed to the goal map.
In order to morph, correspondences between two maps have to be defined.
For example, corresponding points between a pair of polylines have been 
investigated based on 
dynamic programming \citep{mnwb-mpstc-08}, 
Delaunay triangulations and binary line generalized tree (BLG-tree)  
\citep{Deng2015},
and simulated annealing \citep{Li2017_Annealing}.
Between corresponding points, 
straight-line trajectories are often used to interpolate.
\citet{Peng2013_LSA} investigated the problem of defining interpolate 
trajectories 
based on least squares adjustment.
Using morphing, \citet{Peng2016_Admin} continuously generalized between maps of 
administrative boundaries based on compatible triangulations.

@@

Buildings are important elements on maps.
There are many methods of generalizing buildings.
For example, \citet{haunertwolff2010} generalized a set of buildings 
without topological conflicts based an integer program. 
Their method minimizes the number of edges of all the buildings 
and guarantees that the errors are smaller than a user-defined tolerance.
\citet{Buchin2011_Simp} simplified buildings based on an edge-move operation.
One advantage is that their method preserves orientations of the edges.

When users zoom out on digital maps, 
buildings become smaller and the distance between buildings become smaller too. 
In order to make sure that the map is easily perceived, 
an objective proposed by \citet{Weibel1997}, 
some building should be enlarged,
and buildings close to each other should be aggregated.
The process of enlarging and aggregating can be used as a new way 
to compute urban settlement boundaries as did by
\citet{Chaudhry2008}, 
who identified the boundaries based on calculating 'citeness'.
If we have to consider enlarging, simplifying, 
and aggregating buildings simultaneously,
the continuous generalization becomes more complicated.

In our method,

\bigskip

The papers we may review:   
\citet{vanSmaalen2003, Stoter2009},

Our contributions are as follows.
In \sect\ref{sec:Methodology},
we generalize buildings on a start map to obtain buildings on a goal map 
by growing and merging. 
We simplify the buildings on the 
Using the start map and the goal map,
we generate maps at intermediate scales.

a workflow based on compatible
triangulations for generalizing administrative boundaries in a continuous and 
topologically
consistent way; see Section 2.We do a thorough case study with the boundaries
of the counties and the provinces of Mainland China to test the effectiveness
and the efficiency of our method; see Section 3. We conclude in Section 4.

\section{Methodology}
\label{sec:Methodology}
\todo[inline]{a brief introduction of our method.}
We name our input map as start map,
and denote the scale of the start map by $1:M_\mathrm{s}$.
We generate a goal map at scale $1:M_\mathrm{g}$ 
($M_\mathrm{g} > M_\mathrm{s}$) by generalizing the start map. 
We use time $t\in[0,1]$ to define the continuous generalization
process. 
We require that the generalization yields exactly the start map when $t=0$, 
the goal map when $t=1$, 
and that the start map is continuously generalized into the goal map 
when $t$ increases from~$0$ to~$1$.
For the sake of convenience, we define parameter
$M_t= M_\mathrm{s} + t \cdot (M_\mathrm{g}-M_\mathrm{s})$.

@@

%The area of a building on map should be at least $a\,\mathrm{mm}^2$ so that 
%the 
%building is large enough to be perceived.
%In \sect\ref{sec:Simplify}, we show that we set $a=4$.
%Accordingly, a square at the start map should have 
%area $a M_\mathrm{s}^2\,\mathrm{mm}^2$ at least, and
%a square at the goal map should have 
%area $a M_\mathrm{g}^2\,\mathrm{mm}^2$ at least.
%The difference of the side lengths is 
%$\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ 
%(see \fig\ref{fig:Growth}).
%A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
%(M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm}$ so that 
%it can survive when users zoom out from 
%the start map to the goal map.
%In order to eliminate small buildings, 
%we define our growing distance as
%\begin{equation}
%\label{eq:d_G}
%d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} 
%(M_\mathrm{g}-M_\mathrm{s})\,\mathrm{mm} 
%\quad 0 < \lambda <1,
%\end{equation}
%where variable $\lambda$ is a growing factor. 
%A larger $\lambda$ results in  
%fewer buildings to be eliminated, and vice versa.
%During our growing, the growth at time $t$ is
%\begin{equation}
%\label{eq:d_Gt}
%\dtrm{G} = t \cdot d_\mathrm{G}.
%\end{equation}
%
%\begin{figure*}[tb]
%	\centering
%	\includegraphics{Growth}
%	\caption{Growth.}
%	\label{fig:Growth}
%\end{figure*}

@@

\subsection{Merging close buildings by introducing bridges}
\label{sec:Merge}
The distance between two buildings on a map should be larger than a threshold
\citep{Regnauld2001,Li2004}.
Following \citet{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
The real separation distance at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

@@

\section{Conclusion}
\label{sec:Conclusions}

>>>>

Digital maps such as Google Maps and OpenStreetMap 
support zooming by displaying maps at different levels. 
This discrete strategy may results in sudden changes, which annoy users.
To provide better zooming experience, 
we try to produce a sequence of maps 
with small incremental changes from a level to another level.
This process is known as \emph{continuous generalization}.

A way to realize continuous generalization is to use morphing.
Often, a start map and a goal map, 
respectively at a larger scale and a smaller scale, 
are used as input, 
then maps at intermediate scales are produced 
while the start map is morphed to the goal map.
In order to morph, correspondences between two maps need to be defined.
For example, corresponding points between a pair of polylines have been 
investigated based on 
dynamic programming \citep{mnwb-mpstc-08}, 
Delaunay triangulations and binary line generalized tree (BLG-tree)  
\citep{Deng2015},
and simulated annealing \citep{Li2017_Annealing}.
From a point to its corresponding point,
the straight-line trajectory is often used to interpolate.
Using morphing, \citet{Peng2016_Admin} continuously generalized 
administrative boundaries based on compatible triangulations.

@@

Buildings are important elements on maps.
Many methods have been proposed to generalize them.
For example, \citet{haunertwolff2010} simplified a set of buildings 
based an integer program.
Their simplification minimizes the number of edges of all the buildings 
and guarantees that the errors are smaller than a user-defined tolerance.
At the same time, no topological conflict is introduced by the simplification.
\citet{Buchin2011_Simp} simplified buildings based on an edge-move operation.
One advantage is that their method preserves orientations of the edges.
\citet{Chaudhry2008} identified the boundaries of urban settlement by
calculating `citeness' based on buildings.
\citet{Li2017_Building} morphed between two buildings at different scales.
They managed to preserve the orthogonal characteristics of buildings.

When users zoom out on digital maps, 
buildings become smaller and the distances between buildings decrease. 
In order to make sure that the information of a map is easily perceived, 
an objective proposed by \citet{Weibel1997}, 
some building should be enlarged
and buildings close to each other should be aggregated.
Also, buildings should be simplified.
We consider the three operations in our continuous generalization.

Our contributions are as follows.
In \sect\ref{sec:Methodology},
we generalize buildings on a start map to obtain buildings on a goal map.
The generalization consists of aggregating, growing, and simplifying.
We group buildings which will be too close at an output scale.
We aggregate the grouped buildings by introducing bridges.
We grow buildings by buffering,
where we use so-called \emph{miter} joins to keep the right angles of buildings.
Because of using this kind of joins instead of \emph{round} ones,
we have to be more careful.
We show how to solve the problems caused by miter joins.
Eventually, we manage to generate buildings at any intermediate scales.
We carry out a case study in \sect\ref{sec:CaseStudy}
and discuss the performances of our method.
We conclude our paper in \sect\ref{sec:Conclusion}.

\section{Methodology}
\label{sec:Methodology}
We name our input map as start map,
and denote the scale of the start map by $1:M_\mathrm{s}$.
We generate a goal map at scale $1:M_\mathrm{g}$ 
($M_\mathrm{g} > M_\mathrm{s}$) by generalizing the start map. 
We use time $t\in[0,1]$ to define the continuous generalization
process. 
We require that the generalization yields exactly the start map when $t=0$ 
and the goal map when $t=1$.
The start map should be continuously changed to the goal map 
when $t$ increases from~$0$ to~$1$.
For the sake of convenience, we define parameter
$M_t= M_\mathrm{s} + t \cdot (M_\mathrm{g}-M_\mathrm{s})$.

We group buildings which will be too close at time $t$
and aggregate the buildings in the same group by introducing bridges.
We grow the buildings by buffering with miter joins.
Our building simplification consists of two steps.
The first one is to use dilation and erosion to remove pits and spikes.
The second step is to remove vertices using Imai--Iri algorithm.
To make sure that the intermediate-scale buildings never shrink,
we merge the shape of a building with the shape at the previously immediate 
step. 
Also, we clip the building using the shape on goal map.

\subsection{Aggregating close buildings by introducing bridges}
\label{sec:Merge}
The distance between two buildings on a map should be larger than a threshold
\citep{Regnauld2001,Li2004}.
Following \citet{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
The real separation distance at time $t$ is
\begin{equation}
	\label{eq:d_epsilont}
	d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

@@

@@

@@

\section{Conclusion}
\label{sec:Conclusion}
